\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and Sliding Window Filter

### 2014-12-30 Report/project_report.tex

\begin{table*}[t]
  \centering
    \caption{Comparison of Average Root Mean Squared Error (ARMSE), Average Normalized Estimation Error Squared (ANEES), and Compute Time of the MSCKF and SWF on synthetic datasets.}
  \begin{tabular}{*{11}{c}}
              && \multicolumn{4}{c}{MSCKF} & & \multicolumn{4}{c}{SWF} \B \\ \cline{3-6} \cline{8-11}
Feature Count && Pos. ARMSE & Rot. ARMSE & ANEES   & Compute Time && Pos. ARMSE & Rot. ARMSE & ANEES & Compute Time \T\B \\ \hline
40            && 0.2672        & 0.1378        & 10.18  &              && 0.1750        & 0.0495        & 2280 &    \T \\
60            && 0.2550        & 0.1247        & 12.03  &              && 0.1687        & 0.0377        & 2093 &    \\
100           && 0.2304        & 0.0952        & 16.76  &              && 0.1755        & 0.0481        & 2013 &    \B \\ \hline
  \end{tabular}
  \label{tab:rmse_nees}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONCLUSIONS} \label{sec:conclusions}
Based on our experimental results, we conclude that neither the SWF nor the MSCKF is more effective than pure IMU integration in environments with few features.
In environments with more features, both algorithms provide substantial gains over pure IMU integration, although the SWF significantly outperformed the MSCKF in terms of accuracy on the datasets we tested.
However, the accuracy of the MSCKF improves as more features are added, while the SWF is less sensitive to feature quantity.
It is unclear from these results which algorithm would perform best as the number of features grows very large.

>>>>

\begin{table*}[t]
  \centering
    \caption{Comparison of Average Root Mean Squared Error (ARMSE), Average Normalized Estimation Error Squared (ANEES), and Compute Time of the MSCKF and SWF on synthetic datasets.}
  \begin{tabular}{*{11}{c}}
              && \multicolumn{4}{c}{MSCKF} & & \multicolumn{4}{c}{SWF} \B \\ \cline{3-6} \cline{8-11}
Feature Count && Pos. ARMSE    & Rot. ARMSE & ANEES     & Compute Time && Pos. ARMSE   & Rot. ARMSE     & ANEES & Compute Time \T\B \\ \hline
40            && 0.2672        & 0.1378        & 10.18  & 12.19 s      && 0.1750        & 0.0495        & 2280  & 114.3 s   \T \\
60            && 0.2550        & 0.1247        & 12.03  & 14.64 s      && 0.1687        & 0.0377        & 2093  & 175.9 s   \\
100           && 0.2304        & 0.0952        & 16.76  & 20.58 s      && 0.1755        & 0.0481        & 2013  & 245.3 s   \B \\ \hline
  \end{tabular}
  \label{tab:rmse_nees}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONCLUSIONS} \label{sec:conclusions}
Based on our experimental results, we conclude that neither the SWF nor the MSCKF is more effective than pure IMU integration in environments with few features.
In environments with more features, both algorithms provide substantial gains over pure IMU integration, al though the SWF significantly outperformed the MSCKF in terms of accuracy on the datasets we tested.
However, the accuracy of the MSCKF improves as more features are added, while the SWF is less sensitive to feature quantity.
It is unclear from these results which algorithm would perform best as the number of features grows very large.
